Market simulator

### 2020-10-16 analysis/05_market_simulator.Rmd
Changes from our meeting

organization_data <- reactive({
  if (is.null(input$org_update$datapath)) {
    organization_reactive <- read.csv(here::here('analysis', 'output', 'configurations', 'organization_config01.csv'))
    organization_values$file_name = "organization_config01.csv"
    organization_values$file_type = "csv"
    organization_values$file_size = file.size(here::here('analysis', 'output', 'configurations', 'organization_config01.csv'))
    organization_values$file_path = here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
  } else {
    organization_data <- read.csv(input$org_update$datapath)
    organization_values$file_name = input$org_update$name
    organization_values$file_size = input$org_update$size
    organization_values$file_type = input$org_update$type
    organization_values$file_path = input$org_update$datapath
  }
})

@@

```{r org1-inputs}
# Naming
textInput(
  "org1_name",
  label = "Organization Name:",
  value = "Organization 1",
  placeholder = "Enter Organization Name",
  width = "450px"
)
# Organization
renderUI({
  selectInput(
    "org1_org",
    label = "Organization:",
    choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
    # selected = "Red Cross",
    selected = as.character(organization_data()[1:4,][which(organization_data()[1:4,2] == 1), 1]),
    width = "450px"
  )

})

@@

# Issue area
selectInput(
  "org1_issue", 
  label = "Issue Area:",
  choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
  # selected = "Emergency response",
  selected = ifelse(
    sum(organization_data$data[5:7,2]) == 0, "Emergency response",
    as.character(organization_data$data[5:7,][which(organization_data$data[5:7,2] == 1), 1])
  ),
  width = "450px"
)

# Financial transparency
selectInput(
  "org1_fin_trans",
  label = "Financial Transparency:",
  choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
  # selected = "Engages in financial transparency",
  selected = ifelse(
    sum(organization_data$data[8,2]) == 0, "Doesn’t engage in financial transparency",
    as.character(organization_data$data[8,][which(organization_data$data[8,2] == 1), 1])
  ),
  width = "450px"
)

# Financial accountability
selectInput(
  "org1_fin_account",
  label = "Financial Accountability:",
  choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
  # selected = "Engages in financial accountability",
  selected = ifelse(
    sum(organization_data$data[9,2]) == 0, "Doesn’t engage in financial accountability",
    as.character(organization_data$data[9,][which(organization_data$data[9,2] == 1), 1])
  ),
  width = "450px"
)

# Funding sources
selectInput(
  "org1_funding",
  label = "Funding Source:",
  choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
  # selected = "Many small private donations",
  selected = ifelse(
    sum(organization_data$data[10:11,2]) == 0, "Many small private donations",
    as.character(organization_data$data[10:11,][which(organization_data$data[10:11,2] == 1), 1])
  ),
  width = "450px"
)

# Relationship with host government
selectInput(
  "org1_host_gov",
  label = "Relationship With Host Government",
  choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
  # selected = "Friendly relationship with government",
  selected = ifelse(
    sum(organization_data$data[12:13,2]) == 0, "Friendly relationship with government",
    as.character(organization_data$data[12:13,][which(organization_data$data[12:13,2] == 1), 1])
  ),
  width = "450px"
)

>>>>

organization_data <- reactive({
  if (is.null(input$org_update$datapath)) {
    organization_data <- read_csv(here::here('analysis', 'output', 'configurations', 'organization_config01.csv'))
    # organization_values$file_name = "organization_config01.csv"
    # organization_values$file_type = "csv"
    # organization_values$file_size = file.size(here::here('analysis', 'output', 'configurations', 'organization_config01.csv'))
    # organization_values$file_path = here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
  } else {
    organization_data <- read_csv(input$org_update$datapath)
    # organization_values$file_name = input$org_update$name
    # organization_values$file_size = input$org_update$size
    # organization_values$file_type = input$org_update$type
    # organization_values$file_path = input$org_update$datapath
  }
})

@@

```{r org1-inputs}
# Naming
textInput(
  "org1_name",
  label = "Organization Name:",
  value = "Organization 1",
  placeholder = "Enter Organization Name",
  width = "450px"
)
# Organization
renderUI({
  # organization_data = organization_data()
  org_data = organization_data()

  selectInput(
    "org1_org",
    label = "Organization:",
    choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
    # selected = "Red Cross",
    # selected = as.character(organization_data[1:4,][which(organization_data[1:4,2] == 1), 1]),
    selected = as.character(org_data[1:4,][which(org_data[1:4,2] == 1), 1]),
    width = "450px"
  )
})

@@

  # organization_data = organization_data()
  org_data = organization_data()

# Issue area
selectInput(
  "org1_issue", 
  label = "Issue Area:",
  choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
  # selected = "Emergency response",
  selected = ifelse(
    # sum(organization_data$data[5:7,2]) == 0, "Emergency response",
    # as.character(organization_data$data[5:7,][which(organization_data$data[5:7,2] == 1), 1])
    sum(org_data[5:7,2]) == 0, "Emergency response",
    as.character(org_data[5:7,][which(org_data[5:7,2] == 1), 1])
  ),
  width = "450px"
)
})

  # organization_data = organization_data()
  org_data = organization_data()

# Financial transparency
selectInput(
  "org1_fin_trans",
  label = "Financial Transparency:",
  choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
  # selected = "Engages in financial transparency",
  selected = ifelse(
    # sum(organization_data$data[8,2]) == 0, "Doesn’t engage in financial transparency",
    # as.character(organization_data$data[8,][which(organization_data$data[8,2] == 1), 1])
    sum(org_data[8,2]) == 0, "Doesn’t engage in financial transparency",
    as.character(org_data[8,][which(org_data[8,2] == 1), 1])
  ),
  width = "450px"
)

# Financial accountability
selectInput(
  "org1_fin_account",
  label = "Financial Accountability:",
  choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
  # selected = "Engages in financial accountability",
  selected = ifelse(
    # sum(organization_data$data[9,2]) == 0, "Doesn’t engage in financial accountability",
    # as.character(organization_data$data[9,][which(organization_data$data[9,2] == 1), 1])
    sum(org_data[9,2]) == 0, "Doesn’t engage in financial accountability",
    as.character(org_data[9,][which(org_data[9,2] == 1), 1])
  ),
  width = "450px"
)

# Funding sources
selectInput(
  "org1_funding",
  label = "Funding Source:",
  choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
  # selected = "Many small private donations",
  selected = ifelse(
    # sum(organization_data$data[10:11,2]) == 0, "Many small private donations",
    # as.character(organization_data$data[10:11,][which(organization_data$data[10:11,2] == 1), 1])
    sum(org_data[10:11,2]) == 0, "Many small private donations",
    as.character(org_data[10:11,][which(org_data[10:11,2] == 1), 1])
  ),
  width = "450px"
)

# Relationship with host government
selectInput(
  "org1_host_gov",
  label = "Relationship With Host Government",
  choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
  # selected = "Friendly relationship with government",
  selected = ifelse(
    # sum(organization_data$data[12:13,2]) == 0, "Friendly relationship with government",
    # as.character(organization_data$data[12:13,][which(organization_data$data[12:13,2] == 1), 1])
    sum(org_data[12:13,2]) == 0, "Friendly relationship with government",
    as.character(org_data[12:13,][which(org_data[12:13,2] == 1), 1])
  ),
  width = "450px"
)
